\section{Test Design}

The text below describes what we are going to do to test the system, and
includes what we expect as a result for each test. The functional requirements
are repeated here to ease reading. Some of the tests may contain
dependencies\footnotemark. If so, they are specified.

\footnotetext{Even though the functional requirements are independent of
  each other, the tests may be simplified by adding dependencies to other
  functional requirements.}

{\sc Functional Requirement 1}
\begin{Test}
  {\em \FRI}

  {\sc Test:} Create a program which shows a video through a \ac{VGA} port with
  the specified resolution, which runs at at least as many frames per second as
  specified.

  {\sc Pass criteria:} The video shows correctly on the device connected to the
  \ac{VGA} port at the specified number of frames per second.
  
  {\sc Dependencies:} FR3, FR5
\end{Test}

{\sc Functional Requirement 2}
\begin{Test}
  {\em \FRII}
  
  {\sc Test:} Create a program which views a grid of $x \times y$ pixels, each
  corresponding to a cell in Conway's Game of
  Life\cite{gardner1970mathematical}. The game should run at least $N$ turns.

  {\sc Pass criteria:} The Game of Life runs as defined, and is shown properly
  on the device connected to the \ac{VGA} port.

  {\sc Dependencies:} FR3, FR5
\end{Test}

{\sc Functional Requirement 3}
\begin{Test}
  {\em \FRIII}
  
  {\sc Test:} Create a program which utilizes one of the \ac{VGA} ports on the
  board and writes an image to it.

  {\sc Pass criteria:} The image is shown on the device which is connected to
  the \ac{VGA}.
\end{Test}

{\sc Functional Requirement 4}
\begin{Test}
  {\em \FRIV}
  
  {\sc Test:} Create a program for the \ac{SCU} which turns on \acp{LED}
  depending on which button is pressed.

  {\sc Pass criteria:} The \acp{LED} should be lit up when the corresponding
  button is pressed.

  {\sc Dependencies:} FR5
\end{Test}

{\sc Functional Requirement 5}
\begin{Test}
  {\em \FRV}
  
  {\sc Test:} Create a program for the \ac{SCU} which turns the \acp{LED} on in
  a pattern easily recognizable. All \acp{LED} must be utilized at some point
  in the pattern.

  {\sc Pass criteria:} The LEDs lights up in the pattern expected.
\end{Test}

\newpage % Hack to make it look properly
{\sc Functional Requirement 6}
\begin{Test}
  {\em \FRVI}
  
  {\sc Test:} Create one or several assembly programs which together utilizes
  all different aspects of the assembler. Then verify that the programs made
  correspond to the correct instructions through analysis of the output.

  {\sc Pass criteria:} The output generated should correspond to the instruction
  set specification, and should jump to labels correctly.
\end{Test}

{\sc Functional Requirement 7}
\begin{Test}
  {\em \FRVII}
  
  {\sc Test:} Create a $3\times3$ edge detection filter in the instruction set
  of the machine, load it up on the machine along with one or several image
  files or videos, and make it run. It should view the video or image with a
  edge detection filter applied.

  {\sc Pass criteria:} The edge detection filter is visibly applied on the
  image or video chosen.

  {\sc Dependencies:} FR3
\end{Test}

%%% Template below:
%%{\sc Functional Requirement 7}
%%\begin{Test}
%%  {\em \FRI}
%%  {\sc Test:} Foo
%%
%%  {\sc Pass criteria:} Bar
%%\end{Test}
