\section{Test Procedures}

Some of these tests are strictly dependent on other tests. In theory, all the
different tests could be done in any order to test the correctness of the
system. However, some of the functional requirements makes it easy to test other
functional requirements. Therefore, we have decided to let some of these tests
have dependencies. In addition, their ordering is a natural way to approach and
test such a system, mostly because some of the test have a slight overlap. For
instance, it is easier to have example programs if the assembler works
correctly.

{\sc Test 1 - Functional Requirement 5}

{\em \FRV}

\begin{enumerate}
\item Program the \ac{SCU} with a program which lights up the \acp{LED} in every
  binary representation of the numbers 0 to 255.
\item Wait a specified amount of time between \ac{LED} updates. {\sc \color{red}
  TODO: Is this needed?}
\item Verify that the observed pattern is the correct representation of binary
  numbers.
\end{enumerate}

{\sc Test 2 - Functional Requirement 4}

{\em \FRIV}

\begin{enumerate}
\item Program the \ac{SCU} with a program which toggles a \ac{LED} when a button
  is pushed.
\item Verify that the buttons toggle the \acp{LED} when pushed.
\end{enumerate}

{\sc Test 3 - Functional Requirement 6}

{\em \FRVI}

\begin{enumerate}
\item Write a correct program utilizing every available instruction and
  combinations thereof, and run it through the assembler.
\item Use a program such as \tt{hexdump} to verify that the binary output
  corresponds to the specification, and that jump targets are the correct
  addresses.
\end{enumerate}

{\sc Test 4 - Functional Requirement 3}

{\em \FRIII}

\begin{enumerate}
\item Load the \ac{LENA} with a program which copies an image out to the
  \ac{VGA}.
\item Read an image from the \ac{SD} card.
\item Load the image from the \ac{SCU} onto the \ac{LENA}.
\item Start the \ac{LENA}.
\item Verify that the image shows correctly on the screen.
\end{enumerate}

{\sc Test 5 - Functional Requirement 7}

{\em \FRVII}

\begin{enumerate}
\item Foo
\item Baz
\item Spam
\item Egg
\end{enumerate}

{\sc Test 6 - Functional Requirement 1}

{\em \FRI}

\begin{enumerate}
\item Load the \ac{LENA} with a program which copies images out to the \ac{VGA}
  as they are loaded.
\item Read an image from the \ac{SD} card.
\item Load the image onto the \ac{LENA}.
\item Start the \ac{LENA}.
\item Repeat stage 2 to 4 until the video has finished.
\item Measure the frame rate.
\end{enumerate}

{\sc Test 7 - Functional Requirement 2}

{\em \FRII}

\begin{enumerate}
\item Foo
\item Baz
\item Spam
\item Egg
\end{enumerate}
