\section{An Image's Odyssey Through the System}

To summarize the previous sections, let us take a quick example of how the
complete system will process a video, an image or any arbitrary algorithm. 
We will not go into deep details, and as such, some figurative language is
used to simplify complex parts of the system.

At first, the machine is powered up, and all the components wake up from their
sleep. \ac{LENA} will reload its \ac{FPGA} setup from flash, and the \ac{SCU}
will do the same. When these are ready to run, the \ac{SCU} creates a menu and
sends it to \ac{LENA}, which will in turn show the menu through the \ac{VGA} port
it has control over. Whenever a user pushes any of the buttons, the menu is
updated and a new menu image is sent over to \ac{LENA}.

When we have chosen the program to run and the data it should run on, the
\ac{SCU} sets the \ac{LENA} state to a state where it is able to receive
instructions. It then loads the instructions for the given program to
\ac{LENA}. The \ac{SCU} then sets the state to a state where it is able to load
data, before it does exactly that. Finally, the \ac{SCU} allows \ac{LENA} to run. The
  \ac{SCU} will feed \ac{LENA} with more data after some time, depending on what
  data stream we have chosen and what program we have decided to run.

\input{fig/sys-over/journey}

\ac{LENA} now has all it needs to perform its instructions. The control core
starts by activating the \ac{DMA}. The \ac{DMA} starts sending data from memory
to the \ac{SIMD} array. This is done by putting the different values on multiple
``conveyor belts'' which lies below the \ac{SIMD} node. When every \ac{SIMD}
node has data to work with, every node ``picks up'' the data and places it in a
special register.

The control core then sends the instruction the \ac{SIMD} nodes should use
next. In parallel, the \ac{DMA} starts sending in new data into the \ac{SIMD}
nodes, to minimize latency. When the \ac{SIMD} nodes have finished processing
this data, they swap the finished result with the new data on the ``conveyor
belt''. The \ac{DMA} puts on new data, and the finished results are moved on and
out of the ``conveyor belt''. The \ac{DMA} takes the finished result and puts it
back into the data memory.

The control core then takes the results from memory and sends them to the
\ac{VGA} module, which finally sends the image to the device connected to the
\ac{VGA} port. The device, a screen, for instance, then displays the processed
image.

The odyssey has ended for our image, but there is still work to be done. If we
are playing a video, more images will be processed in the way described
above. If we are doing something entirely different | for instance, playing Game
of Life | we may just keep working on the result from last iteration until the
end of time. If we stop before that, the \ac{SCU} will stop \ac{LENA} by turning
its state to a stop state. The \ac{SCU} will then set up the original menu, and
our machine is ready to let new images go on another odyssey with another
program.
