\section{Requirements Specification}
{\em \color{Maroon} We are supposed to write about the (non)functional
  requirements of the project. Not about (non)functional requirements and their
  importance in general, the reader already knows what these are and their
  importance.

 JN: What? How does the reader know about our functional requirements? We made
 them ourselves. If anything, the non-functional requirements are the ones the
 reader knows, as these were specified in the assignment. It's regardless nice
 to sum them up and elaborate what all the requirements mean to our work and how
 we have proceeded.}

% \input{fig/intro/nonfunc}

% Creating a computer without specifying functional requirements would make it
% difficult to both see how well we are progressing and to figure out if we've
% actually reached our goal in the end. Non-functional requirements are
% important to realize the computer: Both price and components were set by the
% assignment as non-functional requirements. As such, both functional and
% non-functional requirements were written down to give ourselves clear goals
% and specifications.

% \input{fig/intro/func}

% Table \ref{fig:func-req}, which shows the functional requirements includes a
% relative priority between the different requirements. This priority tells us
% what we have focused on, as well as what is important in terms of success of
% the computer. Clearly, focusing on performance, as specified in {\sc FR1}, is
% more important than having developer tools for the machine ({\sc FR6}).
% \CHECK{Ensure FR numbers are correct.}  {\sc FR1} ensure the focus on
% performance. {\sc FR2} ensures that we do not end up with a system which is
% not generally programmable. This is important, as a computer specialized for
% image processing has less usability than a generally programmable
% computer. {\sc FR3} and {\sc FR7} makes it easier to show that the computer is
% capable of processing images, whereas {\sc FR4 - FR6} makes it easier to use,
% debug and create programs for the computer.

\input{fig/intro/func} Several functional\TODO{We made the functional
  requirements ourselves, except for ``maybe'' the generally programmable one}
and non-functional requirements were given to us by our instructor, Magnus
Jahre, some were decided by the group as goals we thought were realizable, and
some may help us see how far we are away from our goals. Table
\ref{fig:func-req}, which shows the functional requirements, includes a relative
priority between the different requirements.  This priority tells us what we
have focused on, as well as what is important in terms of success of the
computer. Clearly, focusing on performance, as specified in {\sc FR1}, is more
important than having developer tools for the machine ({\sc FR6}).
\CHECK{Ensure FR numbers are correct.}

{\sc FR1} ensure the focus on performance. {\sc FR2} ensures that we do not end
up with a system which is not generally programmable. This is important, as a
computer specialized for image processing has less usability than a generally
programmable computer. {\sc FR3} and {\sc FR7} makes it easier to show that the
computer is capable of processing images, whereas {\sc FR4 - FR6} makes it
easier to use, debug and create programs for the computer.

\input{fig/intro/nonfunc}

Table \ref{fig:nonfunc-req} shows the non-functional requirements. These were
all determined by the assignment. They are all treated as absolute requirements,
and our design has been centered around those. {\sc NFR1} and {\sc NFR2} gave us
little choice in what hardware to use, and naturally these have been used. {\sc
  NFR3} limits what peripherals we can use to relatively cheap
things.\TODO{``Things'' is not specific enough} {\sc NFR4} constraints our
design choices when designing the image processor. We could not make any set of
SIMD cores\TODO{There's no mentioning of SIMD in the exercise, we could have
  gone MIMD.}, we have to make this specific type. {\sc NFR5} leads to some
design choices for the entire system. Our goal is performance, and we do not
have to care about other concerns such as energy consumption, just to
get\TODO{This has nothing to do with our non-functional requirements. This one
  should be skipped.} performance as good as possible without the system
burning up. However, we may have to sacrifice some simplicity in our design for
the sake of performance.  \ref{fig:nonfunc-req} \TODO{Reference just floating in
  the air?  What is its purpose?}
