\section{Structure of the Report}

This report may be seen as split up in three different parts: chapters
\ref{ch:intro}-\ref{ch:back}, \ref{ch:sys-over}-\ref{ch:pcb} and
\ref{ch:sys-test}-\ref{ch:conc}. \CHECK{Is the chapter numbering correct?} The
current chapter has given you an introduction to the assignment, our goals and
our team. Chapter \ref{ch:back} contains relevant background information for
reading the rest of the report.

Chapters \ref{ch:sys-over} to \ref{ch:pcb} explains in deeper detail {\em how}
the system\TODO{system or machine?} works. Chapter \ref{ch:sys-over} gives an
overview of the whole system and how the different parts are connected
together. Chapter \ref{ch:fpga} deals with how the FPGA parts of the system are
designed: SIMD-nodes, control core as well as the FPGA VGA module is explained
in great detail, along with the interconnection between these. Chapter
\ref{ch:avr} describes the software and structures for the AVR, such as the file
format and the program and data menu. Chapter \ref{ch:pcb} explains the work
around designing the PCB, as well as the soldering and other workarounds we had
to do.

Chapters \ref{ch:sys-test} to \ref{ch:conc} is the conclusion part of the
report. Here we test the system, discuss our choices and present our conclusion,
as well as possible further work. Chapter \ref{ch:sys-test} contains rigorous
tests to check whether we've managed to reach our requirements or not, along
with their results. Chapter \ref{ch:res} describes the result, performance and
energy consumption of the system with different cores and different
programs. Chapter \ref{ch:disc} discusses different choices we did in our
project, and the result of these. In chapter \ref{ch:conc}, our conclusion is
given along with further work.

\TODO{Is this enough, or do we need more elaboration here?}
