\section{Control Module}

The control module is responsible for coordinating the activity of the
other parts of the image processor and for data transfer into and within
the image processor. A visual overview of the control module is given in
figure \ref{fig:control-module}.

\input{fig/fpga/control_module}

The control module decodes the state signal set by the AVR, and enables,
disables and resets components accordingly. It is responsible for performing
data transfers between the AVR and the program/data memories, and for
transferring data internally, between the \ac{SIMD} node array, data \ac{RAM}
and the \ac{VGA} screen buffer.

The control module contains the \ac{CPU} core that is used for the non-\ac{SIMD}
instructions embedded in a program. This \ac{CPU} core, henceforth referred to
as the \emph{control core}, is mainly concerned with loop control, initiating
data transfers between the \ac{SIMD} node array and the data RAM, and copying
image data to the \ac{VGA} controller.

\subsection{States}

The operation of the image processor is fully controlled by the \ac{SCU}. The
\ac{SCU} sets a state value that is used by the control module to select which
components of the image processor are active. This is indicated by the red
signals in figure \ref{fig:control-module}.

The states recognized by the image processor are listed in table
\ref{tab:states}.

\input{fig/fpga/states}

\subsection{Control Core}

A schematic overview of the control core is given in figure
\ref{fig:fpga-ctrl-core}. The control core consists of a register bank
of 21 bit registers, an \ac{ALU} and a connection to the data \ac{RAM}. The word
width of 21 bits was chosen to match the address width of the data \ac{RAM}.
This allows the control core to do pointer arithmetic referring to
arbitrary words in the data \ac{RAM}.

\input{fig/fpga/fpga_ctrl_core}
\TODO{Jahre syntes fig/fpga/fpga\_ctrl\_core ble for liten}
To send pixels to the \ac{VGA} controller, two of the registers are dedicated to
contain an address and a pixel value, respectively. The contents of these
registers are constantly sent to the \ac{VGA} controller. By incrementing and
loading\ac{RAM} values into these registers, using the control core's regular
instruction set, the control core program can upload images to the \ac{VGA}
screen buffer.

A third register is wired to the \ac{DMA} controller, to enable 21 bit wide
\ac{DMA} parameters to be set programmatically.

The control core runs instructions from the same instruction stream as the
\ac{SIMD} nodes, and thus the control core and the \ac{SIMD} array share a
common program counter. The leftmost bit in the instructions specifies whether
the instruction is a control core instruction or a \ac{SIMD} instruction.

The control core instruction set is specified in detail in appendix
\ref{app:control-inst}.

\subsection{DMA Module}

Because of the common instruction stream between the \ac{SIMD} array and the
control core, the \ac{SIMD} array will be inactive whenever the control core is
busy. An important task that normally would be the control core's
responsibility, is to load the \ac{SIMD} array with new data from \ac{RAM} and
to store the processed data back to \ac{RAM}. To maximize the utilization of the
data \ac{RAM} \ac{I/O} capacity and the processing power of the \ac{SIMD} array,
a \emph{Direct Memory Access module} was devised, allowing us to overlap computation
and communication.

The \ac{DMA} module performs loading of new \ac{SIMD} data planes and storing of
processed \ac{SIMD} data planes \emph{in parallell} with the normal execution
of program instructions. The nodes of the \ac{SIMD} array have a separate
register -- the S register -- that is reserved for the \ac{DMA} module. The S
registers are connected in a left-to-right direction throughout the
array. The \ac{DMA} module can send the contents of the S registers one step
to the right by setting a \emph{step S} signal.

With these accommodations of the \ac{SIMD} array, the \ac{DMA} module can load
new data values to the S registers at the left edge of the \ac{SIMD} array, send
the step signal to have these value propagate into the array and read the old,
processed data values from the S registers at the right edge of the array. The
\ac{SIMD} program executing simultaneously will operate on a different set of
registers and will not be obstructed by the \ac{DMA} data transfer.

During \ac{DMA} transfer, the data \ac{RAM} is reserved for the \ac{DMA} module
and not available for the control core. To initiate a \ac{DMA} transfer,
the control core sets \emph{base addresses} for the reading of new data and for
the writing of old data, in addition to address increments to be used for moving
along the columns and rows of the current slice of the data. These parameters
allow flexibility in how the data slices to be loaded into and stored out of the
\ac{SIMD} array, are laid out in memory.
